Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex

We summarize how Path ORAM works in Figure \ref{fig:bintree}. The reader can refer to \cite{PathORAM} for more details. The binary tree is stored on the server. 
Suppose it has height $L$ and $2^L$ leaves. 
The levels are numbered 0 to $L$, where level 0 is the root and level $L$ contains the leaves (in a complete tree). 
Each node in the binary tree is called a bucket, and contains $z$ blocks. 
If a bucket contains less than $z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks after encryption.

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of z = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput as the performance metric, which is a measurement of how fast files can be read from and written to our ORAM-enabled Dropbox. It is expressed in bits per second or multiples of it. For our experiments we use megabytes per second (MB/s).

>>>>

We summarize how Path ORAM works in Figure \ref{fig:bintree}. The reader can refer to \cite{PathORAM} for more details. The binary tree is stored on the server. 
Suppose it has height $L$ and $2^L$ leaves. 
The levels are numbered 0 to $L$, where level 0 is the root and level $L$ contains the leaves (in a complete tree). 
Each node in the binary tree is called a bucket, and contains $Z$ blocks. 
If a bucket contains less than $Z$ “real” blocks, the remainder are composed of dummy blocks, which are indistinguishable from real blocks after encryption.

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of $Z$ = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput as the performance metric, which is a measurement of how fast files can be read from and written to our ORAM-enabled Dropbox. It is expressed in bits per second or multiples of it. For our experiments we use megabytes per second (MB/s).
